To Do List

### 2019-07-10 Papers.Rmd

>>>>

- Mourad, Raphaël, Lang Li, and Olivier Cuvier. “Uncovering Direct and Indirect Molecular Determinants of Chromatin Loops Using a Computational Integrative Approach.” Edited by Alexandre V Morozov. PLOS Computational Biology 13, no. 5 (May 23, 2017): e1005538. https://doi.org/10.1371/journal.pcbi.1005538. - Generalized Linear Model with Interactions (GLMI) to assess TFBSs association with TAD boundaries. 10 versions, each answers different biological question. Log-distance. Biases (fragment length, GC, mappability) are explicitly included. Comparison with enrichment test, correlation, random forest. Outperforms by AUROC. Collinearity and its impact, model with all interactions can account for that. Poisson lasso to regularize. CTCF, RAD21, SMC3, ZNF143, Polycomb proteins, EGR1, ELF1, FOXM1, MAZ, MXI1, NRF1, YY1. Repulsion testing, CTCF and EZH2 are repulsive. Drosophila and human data. https://cran.r-project.org/web/packages/HiCglmi/index.html
